Real-time resolution of short-read assembly graph using ONT long reads

### 2020-07-12 plos_latex_edit.tex
Starting revision

%% END MACROS SECTION

%% npGraph
\newcommand{\npscarf}{$\mathtt{npScarf}$}
\newcommand{\npscarfg}{$\mathtt{npScarf\_wag}$}
\newcommand{\npreader}{$\mathtt{npReader}$}
\newcommand{\npanalysis}{$\mathtt{npAnalysis}$}
\newcommand{\npbarcode}{$\mathtt{npBarcode}$}
\newcommand{\npgraph}{$\mathtt{npGraph}$}
\newcommand{\canu}{$\mathtt{Canu}$}
\newcommand{\unicycler}{$\mathtt{Unicycler}$}
\newcommand{\spades}{$\mathtt{SPAdes}$}
\newcommand{\hspades}{$\mathtt{hybridSPAdes}$}
\newcommand{\albacore}{$\mathtt{Albacore}$}
\newcommand{\racon}{$\mathtt{Racon}$}
\newcommand{\metrichor}{$\mathtt{Metrichor}$}
\newcommand{\minimap}{$\mathtt{minimap2}$}
\newcommand{\miniasm}{$\mathtt{miniasm}$}
\newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}

@@

The first step is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
 define a customised metric which is sample and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage. 
%The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
The metric is then determined by a distance function of two Poisson distributions based on Kullback-Leibler divergence (or relative entropy) between the Poisson distribution representing each contig\cite{Kullback1951information}.

>>>>

%% END MACROS SECTION
\usepackage{cancel}
\newcommand\replace[1]{\textcolor{red}{#1}}
%% npGraph
\newcommand{\npscarf}{$\mathtt{npScarf}$}
\newcommand{\npscarfg}{$\mathtt{npScarf\_wag}$}
\newcommand{\npreader}{$\mathtt{npReader}$}
\newcommand{\npanalysis}{$\mathtt{npAnalysis}$}
\newcommand{\npbarcode}{$\mathtt{npBarcode}$}
\newcommand{\npgraph}{$\mathtt{npGraph}$}
\newcommand{\canu}{$\mathtt{Canu}$}
\newcommand{\unicycler}{$\mathtt{Unicycler}$}
\newcommand{\spades}{$\mathtt{SPAdes}$}
\newcommand{\hspades}{$\mathtt{hybridSPAdes}$}
\newcommand{\albacore}{$\mathtt{Albacore}$}
\newcommand{\racon}{$\mathtt{Racon}$}
\newcommand{\metrichor}{$\mathtt{Metrichor}$}
\newcommand{\minimap}{$\mathtt{minimap2}$}
\newcommand{\miniasm}{$\mathtt{miniasm}$}
\newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}

@@

The first step is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
 define a customised metric which is \cancel{sample} \replace{simple} and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage. 
%The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
The metric is then determined by a distance function of two Poisson distributions based on Kullback-Leibler divergence (or relative entropy) between the Poisson distribution representing each contig\cite{Kullback1951information}.
